Commutative Character Sheaves, with an application to generic types for supercuspidal representations

### 2015-09-03 followup.tex
Small improvements to descent to abelianization section.
Comment about stacks

\begin{proof}
It follows from Lemma~\ref{lem:smooth_coeq} that $q$ is an 
effective descent morphism for the fibred category of commutative character sheaves on smooth group schemes; in other words, the canonical functor $\CCS(G) \to \CCS_{G\der}(G)$ is an equivalence. 
\todo{$\CCS \to \Sch{\Fq}$ is a fibred category. Is it also a stack?}
See appendix for details.
%
Combining this with Proposition~\ref{prop:Gder-equivariant}, it follows that $q^* : \CCS(G\ab)\to \CCS(G)$ is an equivalence.
\end{proof}

>>>>

\begin{proof}
It follows from Lemma~\ref{lem:smooth_coeq} that $q$ is an 
effective descent morphism for the fibred category of commutative character sheaves on smooth group schemes; in other words, the canonical functor $\CCS(G) \to \CCS_{G\der}(G)$ is an equivalence. 
\todo{$\CCS \to \Sch{\Fq}$ is a fibred category. Is it also a stack? That might require a small section, just before this one.}
See appendix for details.
%
Combining this with Proposition~\ref{prop:Gder-equivariance}, it follows that $q^* : \CCS(G\ab)\to \CCS(G)$ is an equivalence.
\end{proof}
